\documentclass[ManualeUtente]{subfiles}

\begin{document}

\chapter{Error reporting}
\section{Before reporting an error}
Before reporting an error it is advisable to check that the problem is due to the software supplied and not to its dependence. In this case, please contact the relevant owner. \\

\subsection{Checklist to verify the problem}
The following are some actions that must be performed before reporting any errors to check if the problem belongs to Marvin or to a dependency.

\begin{itemize}
	\item Check that the Metamask is set to use the correct network. For information on which network to use rely on the guidance offered by your university;
	\item Change the Metamask network on a different network and then return to the correct one;
	\item Close and reopen the browser;
	\item Verify that the requirements are met;
	\item Update your browser and your Metamask plug-in.
\end{itemize}

If after having performed all the previously indicated actions the problem persists then it can be considered an application error and it would be advisable to notify us following the procedure indicated below.

\section{Report an error}
\subsection{DOVE}
EMAIL o ISSUES GITHUB

\subsection{CONVENUTO MESSAGGIO}
-Sito web in uso (Marvin potrebbe essere istanziato più volte) \\
-Proprio ruolo \\
-Passi per far sorgere l'errore \\
-Comportamento di Metamask al sorgere dell'errore (Mostra una finesta? Quantità di gas che segnala? Fallisce?) \\
-Log dalla console (istruzioni Firefox + Chrome) \\
-Eventuali note personali

\end{document}